### 2018-12-01 pilot_manuscript.Rmd
Edited some Method and found info for Exp 2

In order to fully capture the evaluative power of the Moral Foundations Dictionary (MFD; *CITE*), forms and conjugations of words were added to the original MFD. For example, *abuse* was supplemented with *abusive*, *abuser*, *abused*, and *abusing*. Once additional word forms were added, the words making up each of the five foundations in the MFD were split among positive and negative dimensions (i.e., *abide* as a positive authority/respect word and *defect* as a negative authority/respect word).

Once the MFD was separated along lines of positive and negative dimensions for each of the foundations, the article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm]. The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*). The same procedure was applied to the MFD words, and the addition of multiple forms of each concept allowed for the capture of all versions of stemming that might occur given *tm*'s English stemmer function. The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a percentage of their occurrence. Therefore, for each article, the percentage of the number of *harm* (low end) and *care* (high end) related words were calculated and this process was repeated for each of the foundations. This procedure created ten percentages that were included as the dependent variable for the following analyses. 
```{r stem_text, eval=TRUE, include=FALSE}

@@

Kav stuff here

@@

Expected material stuff
- we are going to pick liberal and conservative sources from that thing document linked stuff
- list those here:

- pick a specific date range we want to pull articles from 
- list that here: here's when the stuff was happening and so picked two weeks before and after

>>>>

Using the @Warriner2013 dictionary, the words making up each of the five foundations in the MFD were assigned their respective valence value. Once the MFD words' valences were added to the dataset, the article text was processed using the *tm* and *ngram* packages in *R* in order to render the text in lowercase, remove punctuation, and fix spacing issues [@CITE_tm]. The individual words were then reduced to their stems (i.e., *abused* was stemmed to *abus*). The same procedure was applied to the MFD words and the words in the @Warriner2013 dataset.

DESCRIBE MTMM NEW STUFF HERE? Basically, words found through that project were imported and added to each foundation, with reduncies removed at the end.

The source article words were compiled into a dataset where they were matched up with their counterparts in the MFD along with a percentage of their occurrence and their valence. Therefore, for each article, the percentage of the number of *harm/care* words occurring in the articles were calculated and this process was repeated for each of the foundations. This procedure created five percentages that were included as the dependent variable for the following analyses. 
```{r stem_text, eval=TRUE, include=FALSE}

@@

@@

Expected material stuff
- we are going to pick liberal and conservative sources from that thing document linked stuff
- list those here:
  Sources used by LIBERALS (according to the document thing):
  The New Yorker
  Slate
  The Daily Show (is it wise to use satirical news for this??)
  The Guardian
  Al Jazeera America
  NPR
  New York Times
  Buzzfeed
  PBS
  BBC
  Huffington Post
  Washington Post
  The Economist
  Politico
  MSNBC
  CNN
  NBC News
  CBS News
  Google News
  Bloomberg
  ABC News
  USA TODAY

  Sources used by CONSERVATIVES:
  Fox News
  Drudge Report
  Breitbart
  Rush Limbaugh Show
  The Blaze
  Sean Hannity
  Glenn Beck (does he still report "news"??)

- pick a specific date range we want to pull articles from 
- list that here:

START DATE: September 13, 2018

(September 27, 2018: Ford and Kavanaugh testimony before Senate Judiciary Committee)

END DATE: October 11, 2018

here's when the stuff was happening and so picked two weeks before and after
